Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-02-02 paper.tex
more notes

	In paper \note{Scaling Spark on HPC Systems} it was found that Spark on a Lustre backend performed significantly (4x) slower than that of a workstation using local fast SSDs for storage. This is due to the fact that file system metadata latency (more specifically, file open) is the determinant factor for performance on HPC, whereas network dominates performance in a typical data centre configuration. It was found by the authors that using either a local in-memory filesystem or a filesystem mounted to a single Lustre file improved performance up to the point where it matched that of a workstation. In addition, use of a cache was found to reduce file system metadata operations, and thus improve overall performance. 
	The issues related to using an in-memory filesystem is that it is limited by the amount of physical memory available, and a job will fail if physical memory runs out. Moreover, there is not persistence or resilience of data as it is not saved to non-volatile storage (disk). Spark fails with medium to large applications due to "lax garbage collection in block and shuffle managers". To resolve these issues, the authors first attempted to make all executors share a descriptor pool. This allowed files that were already opened by other executors to be accessed by the executor through the descriptor rather than having to reopen it again. However, the node OS image is subject to number of Inode constraints as well Lustre limits on number of open files for a given job. Due to Inode constraints, a livelock may occur when descriptor pool is at capacity and an executor is attempting to open a file.

	.the authors created mounted a local filesystem backed by a Lustre file \note{requires admin privilege}.
	\note{for each partition, a shuffle file is created and written to as many times as there are partitions. An index file is also created which contains shuffle file locations and offsets. Metadata access is therefore O(partitions2)}

>>>>

	In paper \note{Scaling Spark on HPC Systems} it was found that Spark on a Lustre backend performed significantly (4x) slower than that of a workstation using local fast SSDs for storage. This is due to the fact that file system metadata latency (more specifically, file open) is the determinant factor for performance on HPC, whereas network dominates performance in a typical data centre configuration. It was found by the authors that using either a local in-memory filesystem or a filesystem mounted to a single Lustre file improved performance up to the point where it matched that of a workstation. In addition, use of a cache was found to reduce file system metadata operations, and thus improve overall performance. 
	The issues related to using an in-memory filesystem is that it is limited by the amount of physical memory available, and a job will fail if physical memory runs out. Moreover, there is not persistence or resilience of data as it is not saved to non-volatile storage (disk). Spark fails with medium to large applications due to "lax garbage collection in block and shuffle managers". To resolve these issues, the authors attempted to make all executors share a descriptor pool. This allowed files that were already opened by other executors to be accessed by the executor through the descriptor rather than having to reopen it again. However, the node OS image is subject to number of Inode constraints as well Lustre limits on number of open files for a given job. Due to Inode constraints, a livelock may occur when descriptor pool is at capacity and an executor is attempting to open a file. The authors also created mounted a local filesystem backed by a Lustre file (lustremount) to address the issues related to an in-memory file system \note{requires admin privilege}. It was found that the use of an in-memory file system improved performance by 7.7x and the lustremount improved performance by 6.6x. It was also found that implementation of the filepool improved performance.
	Another issue observed by the authors is that of poor block management as a result of memory constraints resulting in a significant amount of vertical movement. When available memory is exhausted, the least recently used block is evicted by the block-manager. When a call is made to this removed block, it will need to be recomputed, and in the process blocks required for recomputation may also be evicted and necessitate recomputation of those blocks, thus leading to a chain of eviction and recomputation. To resolve this, marking intermediate RDDs as persistent, such that their results are saved to storage instead of requiring recomputation, may be applied.
	\note{they didn't look at improving initial application I/O, though believe that it could be improved with lustremount and filepool. }
	\note{for each partition, a shuffle file is created and written to as many times as there are partitions. An index file is also created which contains shuffle file locations and offsets. Metadata access is therefore O(partitions2)}

	\subsection{tachyon paper}
	Tachyon is an in-memory file system designed to improve read and write performance without impacting fault tolerance of the system. As write performance is impeded by the need to replicate data, Tachyon leverages the concept of lineage to recompute the output if data is lost. Tachyon exhibits 110x faster write throughput than in-memory HDFS and 4.4x faster end-to-end latency. 
	\subsection{triple-H}
